Flesh Simulation in the Field of Animation

### 2020-04-06 LaTeX-Master-Vorlage/chapter/paper.tex
waiting
mimimi

\begin{figure}[!ht]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/lambda_comparison_res.png}  
  \caption{Step 25 with $\lambda = 10.0$}
  \label{fig:res_1}
\end{subfigure}
\begin{subfigure}{.47\textwidth}
  \centering
  % include second image
  \includegraphics[width=.8\linewidth]{resources/lambda_comparison_lambda.png}  
  \caption{Step 25 with $\lambda = 1.0$}
  \label{fig:res_2}
\end{subfigure}
\caption{Results with a different values for $\lambda$ on a hexahedral mesh}
\label{fig:lambda}
\end{figure}

@@

Now instead of decreasing the poisson's ratio, let's increase it. We can achieve that by choosing $\mu = 0.1$ and letting the other variables stay the same as in the first example of this section ($\lambda = 10.0$, res $= 10$). This is an extreme case because the poisson's ratio is very close to $0.5$. A higher poisson's value makes the cube more susceptible for stretching. We can see this effect by comparing the two images in Fig. -.

For solving this system, we need more Newton iterations as we can see in Table \ref{table:mu_tet}  and \ref{table:mu_hex}. This is caused by the more complex deformation. The cube gets a lot narrower in the middle part which increases the difficulty of reaching a solution without artefacts.
\begin{table}[!htbp]
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step size} & \textbf{Iterations} \\ \hline
1 & 2 \\ \hline
2-3 & 3 \\ \hline
4-6 & 4 \\ \hline
7 & 5 \\ \hline
8-11 & 6 \\ \hline
12 & 7 \\ \hline
13-20 & 8 \\ \hline
21-25 & 10 \\ \hline
\end{tabular}
\caption{Newton iterations for a tetrahedral mesh ($\mu = 0.1$)}
\label{table:mu_tet}
}
\hfill
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step size} & \textbf{Iterations} \\ \hline
1 & 5 \\ \hline
2 & 6 \\ \hline
3 & 7 \\ \hline
4 & 8 \\ \hline
5-6 & 9 \\ \hline
7 & 10 \\ \hline
8-9 & 11 \\ \hline
10-11 & 12 \\ \hline
12 & 13 \\ \hline
13-14 & 14 \\ \hline
15 & 15 \\ \hline
16 & 16 \\ \hline
17-19 & 17 \\ \hline
20-25 & 19 \\ \hline
\end{tabular}
\caption{Newton iterations for a hexahedral mesh ($\mu = 0.1$)}
\label{table:mu_hex}
}
\end{table}

@@

@@

\todoredefined[inline]{
TODO: Explain difference in iteration with meshes
}

>>>>

\begin{figure}[!ht]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/lambda_comparison_res.png}  
  \caption{Step 25 with $\lambda = 10.0$}
  \label{fig:lambda_1}
\end{subfigure}
\begin{subfigure}{.47\textwidth}
  \centering
  % include second image
  \includegraphics[width=.8\linewidth]{resources/lambda_comparison_lambda.png}  
  \caption{Step 25 with $\lambda = 1.0$}
  \label{fig:lambda_2}
\end{subfigure}
\caption{Results with a different values for $\lambda$ on a hexahedral mesh}
\label{fig:lambda}
\end{figure}

@@

Now instead of decreasing the poisson's ratio, let's increase it. We can achieve that by choosing $\mu = 0.1$ and letting the other variables stay the same as in the first example of this section ($\lambda = 10.0$, res $= 10$). This is an extreme case because the poisson's ratio is very close to $0.5$. A higher poisson's value makes the cube more susceptible for stretching. We can see this effect a bit by comparing the two images in Fig. \ref{fig:mu}, although the difference is not extreme. The model still behaves well and no artefacts can be seen.

\begin{figure}[!ht]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/mu_res_new.png}  
  \caption{Step 25 with $\mu = 1.0$}
  \label{fig:mu_1}
\end{subfigure}
\begin{subfigure}{.47\textwidth}
  \centering
  % include second image
  \includegraphics[width=.8\linewidth]{resources/mu_mu_new.png}  
  \caption{Step 25 with $\mu = 0.1$}
  \label{fig:mu_2}
\end{subfigure}
\caption{Results with a different values for $\mu$ on a tetrahedral mesh}
\label{fig:mu}
\end{figure}

For solving this system, we need more Newton iterations as we can see in Table \ref{table:mu_tet}  and \ref{table:mu_hex}. This is caused by the more complex deformation. The cube gets narrower in the middle part which increases the difficulty of reaching a valid solution.
\begin{table}[!htbp]
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step size} & \textbf{Iterations} \\ \hline
1 & 2 \\ \hline
2-3 & 3 \\ \hline
4-6 & 4 \\ \hline
7 & 5 \\ \hline
8-11 & 6 \\ \hline
12 & 7 \\ \hline
13-20 & 8 \\ \hline
21-25 & 10 \\ \hline
\end{tabular}
\caption{Newton iterations for a tetrahedral mesh ($\mu = 0.1$)}
\label{table:mu_tet}
}
\hfill
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step size} & \textbf{Iterations} \\ \hline
1 & 5 \\ \hline
2 & 6 \\ \hline
3 & 7 \\ \hline
4 & 8 \\ \hline
5-6 & 9 \\ \hline
7 & 10 \\ \hline
8-9 & 11 \\ \hline
10-11 & 12 \\ \hline
12 & 13 \\ \hline
13-14 & 14 \\ \hline
15 & 15 \\ \hline
16 & 16 \\ \hline
17-19 & 17 \\ \hline
20-25 & 19 \\ \hline
\end{tabular}
\caption{Newton iterations for a hexahedral mesh ($\mu = 0.1$)}
\label{table:mu_hex}
}
\end{table}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.7\textwidth]{resources/mu_extreme_small.png}  
\caption{Results with a different values for $\mu$ on a tetrahedral mesh}
\label{fig:mu_extreme}
\end{figure}

@@

\todoredefined[inline]{
TODO: Explain difference in iteration with meshes. Explain artefacts.
}
